MSPMS Report

### 2024-09-27 README.Rmd
styler

colData_filepath <- system.file("extdata/proteome_discover_colData.csv",
                                package = "mspms")

prepared_pd_data = prepare_pd(peptide_groups_filepath,colData_filepath)

>>>>

colData_filepath <- system.file("extdata/proteome_discover_colData.csv",
  package = "mspms"
)

prepared_pd_data <- prepare_pd(peptide_groups_filepath, colData_filepath)

### 2024-09-27 inst/rmarkdown/templates/mspms_report/skeleton/skeleton.Rmd
styler

```{r}
mspms::plot_nd_peptides(processed_qf)
```
**Figure 2.** Here the library peptides not detected in each samples are shown.

@@

tryCatch({
  print(mspms::plot_all_icelogos(sig_cleavage_data))
}, error = function(e) {
  print(e)
})
```
**Figure 6.** Here the cleavage motifs enriched in each condition are shown. 
Enriched cleavage motifs are defined as having a p.adj <= 0.05 and a log2fc >3
relative to time 0.

>>>>

```{r}
mspms::plot_nd_peptides(processed_qf)
```

**Figure 2.** Here the library peptides not detected in each samples are shown.

@@

tryCatch({
  print(mspms::plot_all_icelogos(sig_cleavage_data))
}, error = function(e) {
  print(e)
})
```

**Figure 6.** Here the cleavage motifs enriched in each condition are shown. 
Enriched cleavage motifs are defined as having a p.adj <= 0.05 and a log2fc >3
relative to time 0.
